### 2025-11-14 course/statml/2025b/project2.tex
Add files via upload

\bibliography{bib}

>>>>

\subsection{Evaluating Machine Learning Methods in Asset Pricing}

\subsubsection{Objective}
This project aims to deepen your understanding of machine learning applications in empirical asset pricing. You will critically engage with the methodology and models proposed in \textit{Chen, L., Pelger, M., \& Zhu, J. (2024). ``Deep Learning in Asset Pricing.'' Management Science, 70(2), 714--750.}  
\href{https://doi.org/10.1287/mnsc.2023.4695}{https://doi.org/10.1287/mnsc.2023.4695}

Specifically, you will replicate the paper's framework %but replace its original \textbf{Generative Adversarial Network (GAN)} model 
and compare it with alternative machine learning methods discussed in \textit{Gu, S., Kelly, B., \& Xiu, D. (2020). ``Empirical Asset Pricing via Machine Learning.'' The Review of Financial Studies, 33(5), 2223--2273.}   \\
\href{https://doi.org/10.1093/rfs/hhaa009}{https://doi.org/10.1093/rfs/hhaa009}

\subsubsection{Tasks}

\begin{enumerate}
    \item \textbf{Reading and Understanding the Original Model}.  
    Carefully read the sections in Chen, Pelger, and Zhu (2024) that describe the machine learning algorithms used, especially the implementation of the GAN-based asset pricing model.  
    Understand how the GAN model learns the stochastic discount factor (SDF) and how the model performance is evaluated.

    \item \textbf{Alternative Machine Learning Implementations}.  
    Refer to Gu, Kelly, and Xiu (2020) for various machine learning approaches used in empirical asset pricing, such as:
    \begin{itemize}
        \item Regularized linear models (e.g., LASSO, Ridge, Elastic Net)
        \item Tree-based models (e.g., Random Forest, Gradient Boosted Trees)
        \item Neural Networks
    \end{itemize}
    Compare the methods from Chen et al. (2024) with these alternative models.  
    Apply appropriate \textbf{hyperparameter tuning methods} (e.g., cross-validation, grid search, random search) as described in Gu et al. (2020).

    \item \textbf{Empirical Evaluation}.  
    Use the same dataset provided by Chen et al. (2024) to ensure comparability.  
    Evaluate the performance of each model in pricing assets using standard metrics such as:
    \begin{itemize}
        \item Sharpe ratio of the estimated SDF
        \item Pricing errors
        \item $R^2$ in cross-sectional tests
    \end{itemize}
    Compare the results of different machine learning methods with the original GAN approach.

    \item \textbf{Resources}.  
    Original code repository:  \\
    \href{https://github.com/jasonzy121/Deep_Learning_Asset_Pricing}{https://github.com/jasonzy121/Deep\_Learning\_Asset\_Pricing}

    Data download link:  \\
    \href{https://drive.google.com/drive/folders/1TrYzMUA_xLID5-gXOy_as8sH2ahLwz-l}{Google Drive Dataset}
\end{enumerate}
\bibliography{bib}
